Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A

### 2016-12-07 draft.tex
Resolved conflict, added title.
Very minor additions to intro, but I am working on it.

\documentclass[nofootinbib,aps,prd,preprint,superscriptaddress]{revtex4}
\usepackage{amsmath,graphicx,hyperref}
\usepackage{slashed}
\usepackage{epstopdf}

@@

\title{Title?}

@@

>>>>

\documentclass[nofootinbib,prd,superscriptaddress,twocolumn]{revtex4}
\usepackage{amsmath,graphicx,hyperref}
\usepackage{slashed}
\usepackage{epstopdf}

@@

\title{Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A}

@@

Dark matter that interacts with itself through a large elastic scattering cross section 
(on the order of $\sigma \sim 10^{-24}\, \mathrm{cm}^2$) 
has been considered for numerous reasons over the past several decades.
